Full Article Review

### 2025-01-08 doc/paper.qmd

As with any research project, things evolve compared to what was
originally intended or planned. In this section we describe what was
changed from the original, uploaded protocol.

### Document types

@@

### Source databases

@@

### Inclusion and exlucion criteria

@@

### Search period

@@

@@

>>>>

This is a scoping review, so we are following the framework described by
Arksey and O'Malley
([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
and by Levac, Colquhoun, and O'Brien
([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
as well as the guidelines outlined in the PRISMA-ScR
([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.

### Deviations from protocol
As with any research project, things evolve compared to what was
originally intended or planned. In this section we describe what was
changed from the original, uploaded protocol.

#### Document types

@@

#### Source databases

@@

#### Inclusion and exlucion criteria

@@

#### Search period

@@

### Formal sources

We developed the initial search strategy in consultation with a research
librarian. We will collect the data via systematic searches of
databases, as well as some hand searches.

We used OpenAlex is an open database with scholarly works from MAG,
Crossref, ORCID, ROR, DOAJ, Unpaywall, Pubmed, Pubmed Central, The ISSN
International Centre, Internet Archive, Web crawls, Subject-area and
institutional repositories from arXiv and Zenodo.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stringr)
library(here)
source(here("R/search-terms.R"))
search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
```

We used the following search terms:

```         
> `r search_terms_inline`
```

Inclusion criteria included any document where open collaboration
practices are not the primary focus. We will be guided by the definition
of open collaboration from Forte and Lampe (2013) mentioned above in
determining whether the records are relevant. Any published document
with reporting on current open collaboration practices. Any published
document with advice, guidance, tools, and/or recommendations for
improving open collaboration. Article language in English.

Exclusion criteria were documents that do not report on specific open
collaboration practices. Documents published \>5 years in the past
(defined as before xxxx) to capture current/most recent practices.

All data obtained from all searches in online databases will be exported
into text files or CVS files for further processing including removal of
duplicates.

At least two of us will extract data using a standardized and tested
template. Data regarding the data source (e.g., author, title,
publication year), open collaboration practices, and any other relevant
information, will be extracted. Extracted data will be summarized with
the descriptive analytical method described by Arksey and O'Malley
(2005). The descriptive analytical method is aimed at identifying and
summarizing different open collaboration practices.

### Informal sources

@@

## Discussion

### 2025-01-08 doc/reviews/luke.qmd

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

-   Very general outline of what they've done, without very clear
    details on how they did it

>>>>

-   Strategies
-   Overview
-   Resources
-   Tools

@@

-   Guide
-   Review

@@

-   They have a website version of their paper, hosted on GitHub, which
    is fantastic to see!

-   The paper doesn't really get into collaboration itself that much,
    just tools that are open and that by default might make it easier to
    collaborate with others.

-   Other terms included: "robustness" when same data but different
    methods give similar results, "generalizable" when new data and new
    methods give similar results when new data and new methods give
    similar results.

-   Reviewed survey says that training and education were major barriers
    to adopting open science practices because of lack of knowledge and
    skill on the tools and processes. And because there are so many new
    tools, it is hard even for experienced researchers to navigate
    everything.

-   The authors have a good strategy for how and why they list the tools
    and resources that they do in the review.

-   BIDS for open neuroimaging data formatting.

-   Hierarchical Events Descriptor (HED) for metadata standard.

-   DataLad for managing data versioning.

@@

-   Training
-   Resources
-   Tools
-   Survey

@@

-   Survey

@@

-   Not a super relevant paper for our review.

-   Related to training, most training material are not created with
    open licenses, which makes it difficult to share and spread and be
    re-used.

-   Training is an area that needs improvement, not enough of it or not
    relevant enough for current situation.

@@

-   Strategies
-   Best practices
-   Review
-   Community-building
-   Training
-   Assessment

@@

-   Useful guidelines for basic strategies to build up open science and
    reproducibility, but not too much on collaboration specifically.

-   Strategies for training:

    -   have more courses on reproducibility and open science
    -   integrate skills in reproducibility and open science into
        existing courses
    -   have more hands-on courses
    -   embed a course training within a research group (e.g. like an
        intervention)
    -   reproduce a study as part of a course group project, to also
        train collaborative team science
    -   require curriculum to include reproducibility and open science
        training

@@

-   Review
-   Tools
-   Best practices

@@

-   Review

@@

-   Is mostly a review of best practices.

-   The content that does get into collaboration is higher level and
    more general, for instance, "collaboration by sending us the data"
    and "we sent out polls to the group to make decisions".

-   Does get into some limitations of doing larger-scale collaborations:

    -   Needs leadership to have progress, so people need to agree on
        who and on how to limit abuse of power and to make decisions
        based on their own preferences or goals without getting input
        from the others
    -   More people means more differences in opinions means more
        potential for conflict.

@@

-   Review
-   Tools

@@

-   This was a very short paper, without anything of relevance to our
    review.

@@

-   Primer
-   Review

@@

-   This paper is very short and has almost nothing about doing open
    research and specifically nothing about open collaboration.

@@

-   Though a bit general, its a good overview of the steps they took to
    get more collaboration going and moving into more openness
